---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

```{r,echo=TRUE}
library(ggplot2)
library(scales)
library(Hmisc)
```

## Loading and preprocessing the data

```{r}
data <- read.csv("activity\\activity.csv")
```

## What is mean total number of steps taken per day?
```{r}
steps_per_day <- aggregate(steps ~ date, data, sum)

hist(steps_per_day$steps, main = "Total Steps per Day", col="Green", xlab="No of Steps")


Steps_mean <- mean(steps_per_day$steps)
steps_median <- median(steps_per_day$steps)

```

The mean is 
```{r,echo=FALSE} 
Steps_mean 
``` 
and the median is  
```{r,echo=FALSE}
steps_median
```
## What is the average daily activity pattern?
```{r}
steps_by_interval <- aggregate(steps ~ interval, data, mean)

plot(steps_by_interval$interval,steps_by_interval$steps, type="l", xlab="Interval", ylab="Number of Steps",main="Average Number of Steps per Day by Interval")


max_interval <-steps_by_interval[which.max(steps_by_interval$steps),1]
```
Most Steps at the interval:
```{r,echo=FALSE}
max_interval
```
## Imputing missing values
```{r}
numMissingValues <- length(which(is.na(data$steps)))
```
Number of missing values:
```{r,echo=FALSE} 
numMissingValues        
```
```{r}
DataImputed <- data
DataImputed$steps <- impute(data$steps, fun=mean)
Imputed_steps_per_day <- aggregate(steps ~ date, DataImputed, sum)
hist(Imputed_steps_per_day$steps, main = paste("Total Steps per Day"), col="Green", xlab="No of Steps")
Imputedmean <- mean(Imputed_steps_per_day$steps)
Imputedmedian <- median(Imputed_steps_per_day$steps)
meandiff<-Imputedmean-Steps_mean
mediandiff<-Imputedmedian-steps_median
stepsdiff<-sum(Imputed_steps_per_day$steps)-sum(steps_per_day$steps)
```
The Imputedmean is 
```{r,echo=FALSE} 
Imputedmean 
``` 
and the Imputedmean is  
```{r,echo=FALSE}
Imputedmedian
```
The mean difference is 
```{r,echo=FALSE}
meandiff
```
The median difference is 
```{r,echo=FALSE}
mediandiff
```
The stepsdiff difference is 
```{r,echo=FALSE}
stepsdiff
```
## Are there differences in activity patterns between weekdays and weekends?
```{r,echo=TRUE}
weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", 
              "Friday")
DataImputed$week = as.factor(ifelse(is.element(weekdays(as.Date(DataImputed$date)),weekdays), "Weekday", "Weekend"))

AverageDataImputed <- aggregate(steps ~ interval + week, data=DataImputed, mean)
ggplot(AverageDataImputed, aes(interval, steps)) + 
    geom_line(color="blue") + 
    facet_wrap(~ week,nrow=2,ncol=1) +
    xlab("5-minute interval") + 
    ylab("Number of steps")+theme_gray()
```

 